% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\author{}
\date{}

\begin{document}

\hypertarget{blueprint-constitution}{%
\section{BLUEPRINT CONSTITUTION}\label{blueprint-constitution}}

Ratified: March 30, 2017

\hypertarget{i.-name}{%
\subsection{I. NAME}\label{i.-name}}

This Constitution recognizes the official name of the organization of
which it represents as ``Blueprint''. This Constitution recognizes that
the organization may also be named under ``Blueprint, Technology for
Nonprofits''.

\hypertarget{ii.-purpose}{%
\subsection{II. PURPOSE}\label{ii.-purpose}}

\hypertarget{mission}{%
\subsubsection{Mission}\label{mission}}

We the members of Blueprint, adhere to and embody our mission to make
beautiful engineering accessible and useful for those who create
communities and promote public welfare.

\hypertarget{vision}{%
\subsubsection{Vision}\label{vision}}

We the members of Blueprint pursue our mission with the vision of a
world where the good, passionate, and visionary have the biggest impact
on our communities and society.

\hypertarget{values}{%
\subsubsection{Values}\label{values}}

We, the members of Blueprint, shall be upheld to the following
organizational values. These values further embody our mission, vision,
and culture, determine how we make decisions, and reflect how we behave
and act, collectively and individually.

\textbf{Mission First:}

We as Blueprint members ultimately unify under one goal - achieving our
mission. We place the interests of the people and partners we serve
above our own. Our primary measure of success is the amount of positive
impact we create through our work.

\textbf{Perpetual Growth:}

We as Blueprint members value the academic, social, and personal growth
of our peers. We constantly seek to perpetuate the cycle of learning and
teaching, for our benefit and for others'. We strive to offer a helping
hand in times of need and push each other to succeed.

\textbf{Cherish Each Other:}

We as Blueprint members seek to cherish our time spent together. We
develop meaningful relationships that extend well beyond the scope of
the organization. We value each other as individuals and appreciate our
differences.

\textbf{Always Innovate:}

We as Blueprint members recognize that change is both inevitable and
necessary. We are committed to innovate and emphasize effective
solutions as needed in order to remain relevant - nothing is sacred. We
welcome new ideas and diverse thinking.

\textbf{Be Humble:}

We as Blueprint members strive to remain humble, accept our
imperfections, and be receptive to feedback. We approach challenges with
an open mind and remember that anyone can pursue social good, not just
Blueprint.

\hypertarget{iii.-membership}{%
\subsection{III. MEMBERSHIP}\label{iii.-membership}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Only currently registered students, faculty, and staff may be active
  members in a registered student organization. Only active members may
  vote or hold office.
\item
  We will not haze according to California State Law. We will not
  restrict membership based upon race, color, national origin, religion,
  sex, gender identity, pregnancy (including pregnancy, childbirth, and
  medical conditions related to pregnancy or childbirth), physical or
  mental disability, medical condition (cancer related or genetic
  characteristics), ancestry, marital status, age, sexual orientation,
  citizenship, or service in the uniformed services (including
  membership, application for membership, performance of service,
  application for service, or obligation for service in the uniformed
  services.)
\item
  The Executive Committee determines the terms of membership and enacts
  them through the bylaws.
\item
  The Executive Committee has the ability to punish its members for
  disorderly behavior, and, with a unanimous vote, expel a member.
\end{enumerate}

\hypertarget{iv.-officers-elections}{%
\subsection{IV. OFFICERS \& ELECTIONS}\label{iv.-officers-elections}}

\hypertarget{executive-committee}{%
\subsubsection{1. Executive Committee}\label{executive-committee}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Executive Committee shall be composed of a President, Internal
  Vice President, External Vice President, Vice President of Projects
  and Vice President of Technology chosen at the end of the previous
  semester by election from the general membership.
\item
  Consent of the Executive Committee is when four-fifths of its members
  agree. The quorum for decision making is four.
\item
  When vacancies happen in the Executive Committee, the Executive
  Committee is responsible to fill such vacancies. When vacancies happen
  in project groups, the Executive Committee is responsible to fill such
  vacancies.
\item
  Each member of the Executive Committee shall be responsible for
  carrying out any duties apart from those below as consented upon by
  the Executive Committee.
\item
  A member of the Executive Committee may only be appointed to the same
  position more than twice if they are elected unopposed.
\item
  Any member of the Executive Committee shall, with the consent of the
  Executive Committee, create chair positions in order to accomplish the
  appointed tasks. Chairs are considered active members but not members
  of the Executive Committee. The appointment, selection, and management
  of those chairs are the sole responsibility of the nominating
  Executive Committee member.
\end{enumerate}

\hypertarget{president}{%
\subsubsection{2. President}\label{president}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The President shall serve as the chief representative of Blueprint and
  its Executive Committee; they shall serve as the main curator and
  protector of the mission and vision of Blueprint; they shall monitor
  the health and well-being of Blueprint, and shall take care that the
  decisions of the Executive Committee be faithfully executed.
\item
  The President shall serve as the main facilitator in any meeting for
  Blueprint.
\item
  The President shall have the power to convene the Executive Committee
  for meetings.
\item
  The President shall have the power to delegate tasks in order to
  accomplish goals set forth by the Executive Committee.
\item
  The President shall at the beginning of the semester give to the
  general membership information of the state and the direction of
  Blueprint, and every general membership meeting give to the general
  membership updates on the state and direction.
\item
  The President shall, with the advice and consent of the Executive
  Committee, commission all of the advisors of Blueprint.
\item
  A member of the Executive Committee shall assume the duties of the
  President in the event of the resignation, recall, or temporary or
  permanent disability of the President to perform his/her duties, until
  such time as a replacement is selected or elected. The order of
  succession is the order in which the offices are stated in the
  constitution: Internal Vice President, External Vice President, Vice
  President of Projects, Vice President of Technology.
\end{enumerate}

\hypertarget{internal-vice-president}{%
\subsubsection{3. Internal Vice
President}\label{internal-vice-president}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Internal Vice President shall serve as the director and manager of
  social and professional activities that are open exclusively to
  Blueprint membership and its alumni.
\item
  The Internal Vice President shall be responsible for obtaining
  facilities for meetings and activities of the Executive Committee.
\item
  The Internal Vice President shall be responsible for management of the
  budget, distributions of funds, and fundraising.
\item
  The Internal Vice President shall, within the fourth week of the
  semester, direct a meeting of the Executive Committee to propose and
  discuss a budget for the semester. The budget must gain consent of the
  Executive Committee to be placed in effect. The Internal Vice
  President is responsible for making sure that the budget is followed
  and not exceeded.
\end{enumerate}

\hypertarget{external-vice-president}{%
\subsubsection{4. External Vice
President}\label{external-vice-president}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The External Vice President shall serve as the director and manager of
  social, professional, and intersocietal activities that Blueprint
  hosts for or conducts with other organizations.
\item
  The External Vice President shall be the main curator of the brand of
  Blueprint. They shall keep the brand and the branding guideline
  current and useful. The enforcement and protection of the brand of
  Blueprint is, with the help from the Executive Committee, the
  responsibility of the External Vice President.
\item
  The External Vice President shall, with the advice and consent of the
  Executive Committee, create a marketing plan for recruitment of
  members by the first week of the semester.
\item
  The External Vice President shall be responsible for the management of
  the External Committee.
\item
  The External Vice President shall, with the advice and consent of the
  Executive Committee, determine the External Committee application
  process by the second week of the semester.
\end{enumerate}

\hypertarget{vice-president-of-projects}{%
\subsubsection{5. Vice President of
Projects}\label{vice-president-of-projects}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Vice President of Projects shall be responsible for the management
  of project groups and relations with client organizations.
\item
  The Vice President of Projects shall, with the advice and consent of
  the Executive Committee, determine the project developer application
  process by the second week of the semester.
\item
  The Vice President of Projects shall, with the advice and consent of
  the Executive Committee, determine project team compositions.
\item
  The Vice President of Projects shall be responsible for maintaining
  faithful and strong relations with past, present, and future
  collaborating organizations.
\end{enumerate}

\hypertarget{vice-president-of-technology}{%
\subsubsection{6. Vice President of
Technology}\label{vice-president-of-technology}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Vice President of Technology is responsible for maintaining
  Blueprint's technological infrastructure.
\item
  The Vice President of Technology is the principle advisor and resource
  of technology for project groups. The Vice President of Technology
  shall appoint advisors as necessary for project groups.
\item
  The Vice President of Technology is responsible for maintaining and
  making available all documentation necessary for the functions of
  Blueprint. This includes documentation for project development,
  Blueprint history and the bylaws.
\end{enumerate}

\hypertarget{elections}{%
\subsubsection{7. Elections}\label{elections}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Every semester, an election must occur to determine the Executive
  Committee for the following term.
\item
  Prior to elections, the Executive Committee shall survey the general
  membership for nominations. A nomination is only invalidated if the
  nominee refuses the nomination.
\item
  During elections, eligible general members will vote. Eligibility will
  be determined by the Executive Committee. Elections shall occur during
  general meeting only with a full quorum of the eligible voting
  membership.
\item
  The Executive Committee shall determine the procedures of nomination
  and campaign in the bylaws.
\end{enumerate}

\hypertarget{v.-meetings}{%
\subsection{V. MEETINGS}\label{v.-meetings}}

\hypertarget{general-member-meetings}{%
\subsubsection{1. General Member
Meetings}\label{general-member-meetings}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The times, places, and manner of all meetings shall be prescribed by
  the Executive Committee.
\item
  Notification methods of all meetings shall be determined by the
  Executive Committee at the beginning of the semester.
\item
  The general membership shall meet every other week. A quorum is
  two-thirds of the general membership. Decisions requiring input from
  the general membership shall be made during the general membership
  meeting.
\end{enumerate}

\hypertarget{executive-committee-meetings}{%
\subsubsection{2. Executive Committee
Meetings}\label{executive-committee-meetings}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Executive Committee shall assemble at least once every week. A
  quorum for meetings is three Executive Committee members.
\end{enumerate}

\hypertarget{special-emergency-meetings}{%
\subsubsection{3. Special Emergency
Meetings}\label{special-emergency-meetings}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Special emergency meetings shall be called on by the President of
  Blueprint for Executive Committee meetings.
\item
  Special emergency meetings shall, with three-fifths approval of the
  Executive Committee, be called on by the President of Blueprint for
  general membership meetings.
\end{enumerate}

\hypertarget{vi.-constitutional-amendments}{%
\subsection{VI. CONSTITUTIONAL
AMENDMENTS}\label{vi.-constitutional-amendments}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Executive Committee, whenever four-fifths of its members shall
  deem it necessary, shall propose Amendments to this Constitution, or,
  on the application of two-thirds of the total membership shall call a
  convention for proposing Amendments, which, in either case, shall be
  valid to all intents and purposes, as part of this Constitution, when
  ratified by three fourths of the total membership.
\item
  All amendments, additions or deletions to this document must be filed
  with the LEAD Center in 432 Eshleman Hall.
\end{enumerate}

\hypertarget{vii.-dissolution}{%
\subsection{VII. DISSOLUTION}\label{vii.-dissolution}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Executive Committee, whenever all of its members shall deem it
  necessary, shall propose the dissolution of this organization and
  Constitution. The dissolution shall be valid to all intents and
  purposes when ratified by all members of the Executive Committee and
  three-fourths of the non-executive membership.
\item
  If the organization is ASUC or GA Sponsored, all unspent ASUC funds
  shall return to the ASUC; all Graduate Assembly funds shall return to
  the Graduate Assembly. If the organization is defunct for five (5) or
  more years, any privately obtained funds (including any funds left in
  miscellaneous accounts) shall be donated to the following nonprofit
  organization: Watsi.
\end{enumerate}

In the event that the designated nonprofit organization no longer exists
or has ceased to be a nonprofit, then the unspent funds shall be donated
to the ASUC.

\hypertarget{viii.-supremacy-oaths}{%
\subsection{VIII. SUPREMACY \& OATHS}\label{viii.-supremacy-oaths}}

\hypertarget{supremacy}{%
\subsubsection{1. Supremacy}\label{supremacy}}

This Constitution shall be the supreme law of Blueprint.

\hypertarget{oaths}{%
\subsubsection{2. Oaths}\label{oaths}}

All members of Blueprint shall be bound by contract and oath to support
this Constitution until the end or termination of membership.

\hypertarget{bylaws}{%
\subsubsection{3. Bylaws}\label{bylaws}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  All procedures and operations specified by the Constitution may not be
  changed except by constitutional amendment. All procedures and
  operations not specified by the Constitution that the Executive
  Committee deems necessary for current and future members to abide by
  may be determined by the Executive Committee through the bylaws.
\item
  The bylaws must be made readily available to the general membership
  through permanent and accessible documentation. This documentation
  should record both the current and past bylaws.
\item
  A four-fifths majority of the Executive Committee is necessary to
  enact a bylaw.
\item
  A four-fifths majority of the Executive Committee is necessary to
  overturn a bylaw.
\item
  Any enacted or overturned bylaw must be presented at the soonest
  general meeting. Changes made to the bylaws must be reflected in the
  documentation within 24 hours.
\end{enumerate}

\hypertarget{ratification}{%
\subsubsection{4. Ratification}\label{ratification}}

The Ratification of three fourths majority of Blueprint members shall be
sufficient for the establishment of this Constitution.

\end{document}
