\documentclass{article}

\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{listings}
\usepackage[parfill]{parskip}
\usepackage{titlesec}
\setcounter{secnumdepth}{-1}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\title{CONSTITUTION}

\author{\\ \sc BLUEPRINT}
\date{Ratified: March 20, 2017 }

\begin{document}

\maketitle

\section{I. NAME}
This Constitution recognizes the official name of the organization of which it represents as ``Blueprint". This Constitution recognizes that the organization may also be named under ``Blueprint, Technology for Nonprofits".

\section{II. PURPOSE}
\subsection{1. Mission}
We the members of Blueprint, adhere to and embody our mission to make beautiful engineering accessible and useful for those who create communities and promote public welfare.

\subsection{2. Vision}
We the members of Blueprint pursue our mission with the vision of a world where the good, passionate, and visionary have the biggest impact on our communities and society.


\subsection{3. Values}
We, the members of Blueprint, shall be upheld to the following organizational values. These values further embody our mission, vision, and culture, determine how we make decisions, and reflect how we behave and act, collectively and individually.

\textbf{Mission First:}

We as Blueprint members ultimately unify under one goal -  achieving our mission. We place the interests of the people and partners we serve above our own. Our primary measure of success is the amount of positive impact we create through our work.

\textbf{Perpetual Growth:}

We as Blueprint members value the academic, social, and personal growth of our peers. We constantly seek to perpetuate the cycle of learning and teaching, for our benefit and for others’. We strive to offer a helping hand in times of need and push each other to succeed.

\textbf{Cherish Each Other:}

We as Blueprint members seek to cherish our time spent together. We develop meaningful relationships that extend well beyond the scope of the organization. We value each other as individuals and appreciate our differences.

\textbf{Always Innovate:}

We as Blueprint members recognize that change is both inevitable and necessary. We are committed to innovate and emphasize effective solutions as needed in order to remain relevant - nothing is sacred. We welcome new ideas and diverse thinking.

\textbf{Be Humble:}

We as Blueprint members strive to remain humble, accept our imperfections, and be receptive to feedback. We approach challenges with an open mind and remember that anyone can pursue social good, not just Blueprint. 

 
\section{III. MEMBERSHIP}

\textbf{1.} Only currently registered students, faculty, and staff may be active members in a registered student organization. Only active members may vote or hold office.

\textbf{2.} We will not haze according to California State Law. We will not restrict membership based upon race, color, national origin, religion, sex, gender identity, pregnancy (including pregnancy, childbirth, and medical conditions related to pregnancy or childbirth), physical or mental disability, medical condition (cancer related or genetic characteristics), ancestry, marital status, age, sexual orientation, citizenship, or service in the uniformed services (including membership, application for membership, performance of service, application for service, or obligation for service in the uniformed services.)

\textbf{3.} The Executive Committee determines the terms of membership and enacts them through the bylaws. 

\textbf{4.} The Executive Committee has the ability to punish its members for disorderly behavior, and, with a unanimous vote, expel a member.

\section{IV. OFFICERS \& ELECTIONS}
\subsection{1. Executive Committee}
\textbf{1.} The Executive Committee shall be composed of a President, Internal Vice President, External Vice President, Vice President of Projects and Vice President of Technology chosen at the end of the previous semester by election from the general membership.

\textbf{2.} Consent of the Executive Committee is when four-fifths of its members agree. The quorum for decision making is four.

\textbf{3.} When vacancies happen in the Executive Committee, the Executive Committee is responsible to fill such vacancies. When vacancies happen in project groups, the Executive Committee is responsible to fill such vacancies.

\textbf{4.} Each member of the Executive Committee shall be responsible for carrying out any duties apart from those below as consented upon by the Executive Committee.

\textbf{5.} A member of the Executive Committee may only be appointed to the same position more than twice if they are elected unopposed.

\textbf{6.} Any member of the Executive Committee shall, with the consent of the Executive Committee, create chair positions in order to accomplish the appointed tasks. Chairs are considered active members but not members of the Executive Committee. The appointment, selection, and management of those chairs are the sole responsibility of the nominating Executive Committee member.

\subsection{2. President}

\textbf{1.} The President shall serve as the chief representative of Blueprint and its Executive Committee; they shall serve as the main curator and protector of the mission and vision of Blueprint; they shall monitor the health and well-being of Blueprint, and shall take care that the decisions of the Executive Committee be faithfully executed.

\textbf{2.} The President shall serve as the main facilitator in any meeting for Blueprint.

\textbf{3.} The President shall have the power to convene the Executive Committee for meetings.

\textbf{4.} The President shall have the power to delegate tasks in order to accomplish goals set forth by the Executive Committee.

\textbf{5.} The President shall at the beginning of the semester give to the general membership information of the state and the direction of Blueprint, and every general membership meeting give to the general membership updates on the state and direction.

\textbf{6.} The President shall, with the advice and consent of the Executive Committee, commission all of the advisors of Blueprint.

\textbf{7.} A member of the Executive Committee shall assume the duties of the President in the event of the resignation, recall, or temporary or permanent disability of the President to perform his/her duties, until such time as a replacement is selected or elected. The order of succession is the order in which the offices are stated in the constitution: Internal Vice President, External Vice President, Vice President of Projects, Vice President of Technology. 

\subsection{3. Internal Vice President}

\textbf{1.} The Internal Vice President shall serve as the director and manager of social and professional activities that are open exclusively to Blueprint membership and its alumni.

\textbf{2.} The Internal Vice President shall be responsible for obtaining facilities for meetings and activities of the Executive Committee.

\textbf{3.} The Internal Vice President shall be responsible for management of the budget, distributions of funds, and fundraising.

\textbf{4.} The Internal Vice President shall, within the fourth week of the semester, direct a meeting of the Executive Committee to propose and discuss a budget for the semester. The budget must gain consent of the Executive Committee to be placed in effect. The Internal Vice President is responsible for making sure that the budget is followed and not exceeded.

\subsection{4. External Vice President}

\textbf{1.} The External Vice President shall serve as the director and manager of social, professional, and intersocietal activities that Blueprint hosts for or conducts with other organizations. 

\textbf{2.} The External Vice President shall be the main curator of the brand of Blueprint. They shall keep the brand and the branding guideline current and useful. The enforcement and protection of the brand of Blueprint is, with the help from the Executive Committee, the responsibility of the External Vice President.

\textbf{4.} The External Vice President shall, with the advice and consent of the Executive Committee, create a marketing plan for recruitment of members by the first week of the semester.

\textbf{5.} The External Vice President shall be responsible for the management of the External Committee.

\textbf{6.} The External Vice President shall, with the advice and consent of the Executive Committee, determine the External Committee application process by the second week of the semester.

\subsection{5. Vice President of Projects}

\textbf{1.} The Vice President of Projects shall be responsible for the management of project groups and relations with client organizations.

\textbf{2.} The Vice President of Projects shall, with the advice and consent of the Executive Committee, determine the project developer application process by the second week of the semester.

\textbf{3.} The Vice President of Projects shall, with the advice and consent of the Executive Committee, determine project team compositions.

\textbf{4.} The Vice President of Projects shall be responsible for maintaining faithful and strong relations with past, present, and future collaborating organizations.

\subsection{6. Vice President of Technology}

\textbf{1.} The Vice President of Technology is responsible for maintaining Blueprint's technological infrastructure.

\textbf{2.} The Vice President of Technology is the principle advisor and resource of technology for project groups. The Vice President of Technology shall appoint advisors as necessary for project groups.

\textbf{3.} The Vice President of Technology is responsible for maintaining and making available all documentation necessary for the functions of Blueprint. This includes documentation for project development, Blueprint history and the bylaws.

\subsection{7. Elections}
\textbf{1.} Every semester, an election must occur to determine the Executive Committee for the following term. 

\textbf{2.} Prior to elections, the Executive Committee shall survey the general membership for nominations. A nomination is only invalidated if the nominee refuses the nomination.

\textbf{3.} During elections, eligible general members will vote. Eligibility will be determined by the Executive Committee. Elections shall occur during general meeting only with a full quorum of the eligible voting membership.

\textbf{4.} The Executive Committee shall determine the procedures of nomination and campaign in the bylaws.

\section{V. MEETINGS}
\subsection{1. General Member Meetings}
\textbf{1.} The times, places, and manner of all meetings shall be prescribed by the Executive Committee.

\textbf{2.} Notification methods of all meetings shall be determined by the Executive Committee at the beginning of the semester.

\textbf{2.} The general membership shall meet every other week. A quorum is two-thirds of the general membership. Decisions requiring input from the general membership shall be made during the general membership meeting.

\subsection{2. Executive Committee Meetings}
\textbf{1.} The Executive Committee shall assemble at least once every week. A quorum for meetings is three Executive Committee members.

\subsection{3. Special Emergency Meetings}
\textbf{1.} Special emergency meetings shall be called on by the President of Blueprint for Executive Committee meetings.

\textbf{2.} Special emergency meetings shall, with three-fifths approval of the Executive Committee, be called on by the President of Blueprint for general membership meetings.

\section{VI. CONSTITUTIONAL AMENDMENTS}
\textbf{1.} The Executive Committee, whenever four-fifths of its members shall deem it necessary, shall propose Amendments to this Constitution, or, on the application of two-thirds of the total membership shall call a convention for proposing Amendments, which, in either case, shall be valid to all intents and purposes, as part of this Constitution, when ratified by three fourths of the total membership.

\textbf{2.} All amendments, additions or deletions to this document must be filed with the LEAD Center in 432 Eshleman Hall.

\section{VII. DISSOLUTION}
\textbf{1.} The Executive Committee, whenever all of its members shall deem it necessary, shall propose the dissolution of this organization and Constitution. The dissolution shall be valid to all intents and purposes when ratified by all members of the Executive Committee and three-fourths of the non-executive membership.

\textbf{2.} If the organization is ASUC or GA Sponsored, all unspent ASUC funds shall return to the ASUC; all Graduate Assembly funds shall return to the Graduate Assembly. If the organization is defunct for five (5) or more years, any privately obtained funds (including any funds left in miscellaneous accounts) shall be donated to the following nonprofit organization: Watsi.

In the event that the designated nonprofit organization no longer exists or has ceased to be a nonprofit, then the unspent funds shall be donated to the ASUC.

\section{VIII. SUPREMACY \& OATHS}
\subsection{1. Supremacy}
This Constitution shall be the supreme law of Blueprint.

\subsection{2. Oaths}
All members of Blueprint shall be bound by contract and oath to support this Constitution until the end or termination of membership.

\subsection{3. Bylaws}
\textbf{1.} All procedures and operations specified by the Constitution may not be changed except by constitutional amendment. All procedures and operations not specified by the Constitution that the Executive Committee deems necessary for current and future members to abide by may be determined by the Executive Committee through the bylaws. 

\textbf{2.} The bylaws must be made readily available to the general membership through permanent and accessible documentation. This documentation should record both the current and past bylaws.

\textbf{3.} A four-fifths majority of the Executive Committee is necessary to enact a bylaw.

\textbf{4.} A four-fifths majority of the Executive Committee is necessary to overturn a bylaw.

\textbf{5.} Any enacted or overturned bylaw must be presented at the soonest general meeting. Changes made to the bylaws must be reflected in the documentation within 24 hours.

\subsection{4. Ratification}
The Ratification of three fourths majority of Blueprint members shall be sufficient for the establishment of this Constitution.
\end{document}